---
title: "Sardine MSE Result Notes"
author: "Robert Wildermuth"
date: "7/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
library(r4ss)
source("plot_comp_sampling.R")
```

# Evaluation of sardine cohort growth operating model

The following notes document the results of applying a 6 year projection to Peter Kuriyama's cohort growth Stock Synthesis model for Pacific sardine using {SSMSE}. The separate runs progress from a self test to applying additional sampling error in the SSMSE sampling module.

## Self test with only acoustic-trawl index specified

```{r OMselftest}
# read in SSMSE results summary
tsSumry <- read.csv("C:/Users/rwildermuth/Documents/FutureSeas/SardineMSE/cohortGrowthOMandEM/cohortGrowthselftest/results_ts_cohortGrowthselftest.csv")

# Get rid of duplicated SSB years
tsSumry <- na.omit(tsSumry)

# plots of simulated and estimated biomass trends per iteration
ggplot2::ggplot(data = subset(tsSumry, model_run %in% c("0_estimate_cohort_growh_OM",  
                                                      "cohortGrowthOMandEM_EM_2020",
                                                      "cohortGrowthOMandEM_EM_2021",
                                                      "cohortGrowthOMandEM_EM_2022",
                                                      "cohortGrowthOMandEM_EM_2023",
                                                      "cohortGrowthOMandEM_EM_2024")), 
                ggplot2::aes(x = year, y = SpawnBio)) +
  ggplot2::geom_vline(xintercept = 2019, color = "gray") +
  ggplot2::geom_line(ggplot2::aes(linetype = as.character(iteration), color = model_run))+
  ggplot2::scale_color_manual(values = c("#D65F00", rep("black", 4), "blue")) +
  ggplot2::scale_linetype_manual(values = rep("solid", 50)) +
  ggplot2::guides(linetype = FALSE) +
  ggplot2::facet_wrap(. ~ iteration) +
  ggplot2::theme_classic()

```

Summary plots of terminal year estimates
```{r}
termYr <- tsSumry %>% filter(model_run %in% c("0_estimate_cohort_growh_OM", 
                                              "cohortGrowthOMandEM_EM_init") | # or keep end years
                             year == as.numeric(regmatches(model_run, 
                                                           gregexpr("[[:digit:]]+", model_run))))

termYr <- termYr %>% mutate(model_run = as.character(model_run),
                            model_run = case_when(!model_run %in% c("0_estimate_cohort_growh_OM", 
                                                                    "cohortGrowthOMandEM_EM_init") ~"cohortGrowthOMandEM_EM_term",
                                                  TRUE ~ model_run))

ggplot2::ggplot(data = termYr, 
                ggplot2::aes(x = year, y = SpawnBio)) +
  ggplot2::geom_vline(xintercept = 2019, color = "gray") +
  ggplot2::geom_line(ggplot2::aes(linetype = as.character(iteration), color = model_run))+
  ggplot2::scale_color_manual(values = c("#D65F00", "black", rep("blue", 5))) +
  ggplot2::scale_linetype_manual(values = rep("solid", 50)) +
  ggplot2::guides(linetype = FALSE) +
  ggplot2::facet_wrap(. ~ iteration) +
  ggplot2::theme_classic()

relSSB_EMtoOM <- termYr %>% select(model_run, year, iteration, SpawnBio) %>%
                    pivot_wider(id_cols = c(year, iteration),
                                names_from = model_run, values_from = SpawnBio) %>%
                    rename(cohort_growth_OM = "0_estimate_cohort_growh_OM") %>%
                    mutate(diffSSB = case_when(is.na(cohortGrowthOMandEM_EM_term) ~ cohortGrowthOMandEM_EM_init - cohort_growth_OM,
                                               !is.na(cohortGrowthOMandEM_EM_term) ~ cohortGrowthOMandEM_EM_term - cohort_growth_OM))

ggplot(data = relSSB_EMtoOM, aes(x = year, y = diffSSB)) +
  ggplot2::geom_vline(xintercept = 2019, color = "gray") +
  geom_hline(yintercept = 0, color = "black") +
  ggplot2::geom_line(ggplot2::aes(linetype = as.character(iteration), color = 2))+
  #ggplot2::scale_color_manual(values = c("#D65F00", "black", rep("blue", 5))) +
  ggplot2::scale_linetype_manual(values = rep("solid", 50)) +
  ggplot2::guides(linetype = FALSE) +
  ggplot2::facet_wrap(. ~ iteration) +
  ggplot2::theme_classic()
```

Plots of length and age composition
```{r}
plot_comp_sampling(dir = "C:/Users/rwildermuth/Documents/FutureSeas/SardineMSE/cohortGrowthOMandEM/cohortGrowthselftest", comp_type = "agecomp")

outputSS <- SS_output(
  dir = "C:/Users/rwildermuth/Documents/FutureSeas/SardineMSE/cohortGrowthOMandEM/cohortGrowthselftest/2/cohortGrowthOMandEM_EM_2024",
  dir.mcmc = NULL,
  repfile = "Report.sso",
  compfile = "CompReport.sso")

SSplotComps(replist = outputSS, kind = "LEN")

SSplotComps(replist = outputSS, kind = "AGE") # nothing happens


```